Stagnating State Funding for Higher Education and its Effect on Faculty at US Universities

### 2023-07-18 text/paper.tex
Revision 2 finished (though needs check over of writing).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Title page
% Author
\author{Senan Hogan-Hennessy\thanks{
        For helpful comments I thank
        Levon Barseghyan,
        Francine Blau,
        Ryan Dycus,
        Ronald Ehrenberg,
        Michael Lovenheim,
        Jake Meyer,
        Douglas Miller,
        and Evan Riehl,
        as well as seminar participants at Cornell University (Autumn 2022) for helpful discussion.} \\
    \vspace{0.1cm}
    Economics Department, Cornell University
}
% Title
\title{Stagnating State Funding for Higher Education and its Effect on Faculty at US Universities
    }
\date{This version: \today\thanks{
    This project's Github repository, with materials and anonymised data for replication, is available at 
    \url{https://github.com/shoganhennessy/state-funding-faculty}.
    Any comments or suggestions may be sent to me at \href{mailto:seh325@cornell.edu}{\nolinkurl{seh325@cornell.edu}}, or raised as an issue on the Github project.
    } \\ \vspace{0.1cm}
    \href{https://github.com/shoganhennessy/state-funding-faculty/blob/main/https://github.com/shoganhennessy/state-funding-faculty-2023.pdf}{Newest version available here.}
}
\rhead{\today}
\lhead{Stagnating State Funding for Higher Education and its Effect on Faculty.}
% Begin
\begin{document}
\maketitle
\thispagestyle{empty}
% Abstract
\begin{abstract}
    \noindent
    \input{sections/00-abstract.tex}
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Title page
% Author
\author{Senan Hogan-Hennessy\thanks{
        For helpful comments I thank
        Levon Barseghyan,
        Francine Blau,
        Ryan Dycus,
        Ronald Ehrenberg,
        Michael Lovenheim,
        Jake Meyer,
        Douglas Miller,
        and Evan Riehl,
        as well as seminar participants at Cornell University (Autumn 2022) for helpful discussion.} \\
    \vspace{0.1cm}
    Economics Department, Cornell University
}
% Title
\title{Stagnating State Funding for Higher Education and its Effect on Faculty at US Universities
    }
\date{This version: \today\thanks{
    This project's Github repository, with materials and anonymised data for replication, is available at 
    \url{https://github.com/shoganhennessy/state-funding-faculty}.
    Any comments or suggestions may be sent to me at \href{mailto:seh325@cornell.edu}{\nolinkurl{seh325@cornell.edu}}, or raised as an issue on the Github project.
    } \\ \vspace{0.1cm}
    \href{https://github.com/shoganhennessy/state-funding-faculty/blob/main/state-funding-faculty-2023.pdf}{Newest version available here.}
}
\rhead{\today}
\lhead{Stagnating State Funding for Higher Education and its Effect on Faculty.}
% Begin
\begin{document}
\maketitle
\thispagestyle{empty}
% Abstract
\begin{abstract}
    \noindent
    \input{sections/00-abstract.tex}
\end{abstract}

### 2023-07-18 text/sections/01-introduction.tex
Revision 2 finished (though needs check over of writing).

Mine is the first paper to provide causal evidence on the impact of state funding on faculty composition, and wages.
The closest related research on higher education funding has examined how university spending affected graduation rates and levels of student debt \citep{NBERw23736,NBERw27885}, and university finances \citep{miller2022making,bound2019public,brown2014endowment}.
For faculty outcomes, multiple theoretically model university decision-making and faculty hiring (see e.g., \citealt{abe2015implications,johnson2009jep,NBERc13879}), while others measured how faculty at universities were affected by endowment shocks and the 2008 recession \citep{brown2014endowment,turner2014impact}.
These papers measure effects of funding and changes in university revenues, but not measure effects on faculty, or other outcomes related to university instruction.

>>>>

Mine is the first paper to provide causal evidence on the impact of state funding on faculty composition, and wages.
The closest related research on higher education funding has examined how university spending affected graduation rates and levels of student debt \citep{NBERw23736,NBERw27885}, and university finances \citep{miller2022making,bound2019public,brown2014endowment}.
For faculty outcomes, multiple theoretically model university decision-making and faculty hiring (see e.g., \citealt{abe2015implications,johnson2009jep,NBERc13879}), while others measured how faculty at universities were affected by endowment shocks and the 2008 recession \citep{brown2014endowment,turner2014impact}.
These papers measure effects of funding and changes in university revenues, but do not measure effects on faculty, or other outcomes related to university instruction.
